TADCompare: an R package for differential analysis and characterization of Topologically Associated Domains

### 2019-10-19 manuscript/manuscript.Rmd
Add Carl's wording

The coherence measure allows us to gain insights into the genetic component of various phenotypes, as revealed by the current state of the corresponding GWASs. The high coherence of metabolic diseases and traits is suggestive of the strong genetic component driving molecular mechanisms of metabolism-specific gene networks. On the contrary, the low coherence of a phenotype suggests either insufficient knowledge of genetics or the true lack of genetic influence. The insufficient knowledge may be remedied by identifying novel genes through larger-scale GWASs and meta-analyses. However, the lack of genetic influence will continue to be reflected in low coherence measures irrespectively of the number of genes. Our results highlight the low coherence of the molecular mechanisms of intelligence-related traits, cardiovascular and psychiatric disorders, but cannot answer whether insufficient knowledge or the lack of genetic component drives it.

>>>>

The coherence measure allows us to gain insights into the genetic component of various phenotypes, as revealed by the current state of the corresponding GWASs. The high coherence of metabolic diseases and traits arguably reflects the strong genetic component driving molecular mechanisms of metabolism-specific gene networks. On the contrary, the low coherence of a phenotype suggests either insufficient knowledge of genetics (as represented in current-generation databases) or the true lack of such a strong genetic influence, (and correspondingly, the heightened importance in these cases of non-genetic, and possibly environmental, factors. If the incoherence results from insufficient knowledge, this should be remedied as novel genes are identified through larger-scale GWASs and meta-analyses. Yet, the low coherence of a phenotype is expected to remain low with increasing gene discovery if, in contrast, the absence of coherence is due to the relative importance of non-genetic causes. Our results highlight the low coherence of the molecular mechanisms of intelligence-related traits and cardiovascular and psychiatric disorders, but our method alone cannot decide whether insufficient knowledge or the weakness of the genetic component ultimately explains the lack of internal connectivity characteristic of low-coherence traits.
